A free/open-source Kazakh-Tatar machine translation system

### 2013-02-27 paper/paper.tex
add few words about Tatar
some more

\title{A prototype machine translation system for Kazakh and Tatar based on 
   free/open-source components}

@@

\abstract{
This paper presents a prototype bidirectional machine translation system between 
Kazakh and Tatar.
 \\
\Keywords{Kazakh, Tatar, MT, Free software, Open-source}
}

@@

Both languages belong to the Kypchak (or Northwestern) group of Turkic languages.
Kazakh is primarily spoken in Kazakhstan, where it is the national language. Large
groups of native speakers also exist in neigbouring Central-Eurasian republics,
China and Mongolia. Total number of speakers is at least 10 million people.

@@

Several previous works on making machine translation systems between 
Turkic languages exist, although to our knowledge none are publically available.

For systems between Turkish and other Turkic languages, there have been, 
for example, systems reported for Turkish-Crimean Tatar \citep{altintas01}, Turkish-Azerbaijani \citep{hamzaoglu93}, Turkish-Tatar \citep{suleymanov08}, and Turkish-Turkmen \citep{tantug07}.

>>>>

\title{A free/open-source Kazakh-Tatar machine translation system}

@@

\abstract{
This paper presents a bidirectional machine translation system between
Kazakh and Tatar.
 \\
\Keywords{Kazakh, Tatar, MT, Free software, Open-source}
}

@@

Both languages belong to the Kypchak (or Northwestern) group of Turkic
languages. Kazakh is primarily spoken in Kazakhstan, where it is the national
language. Large groups of native speakers also exist in China, neigbouring
Central-Eurasian republics and Mongolia. Total number of speakers is at least
10 million people. Tatar is a Turkic language spoken in and around Tatarstan by
approximately 6 million people. It is co-official with Russian in Tatarstan --
a republic within Russia.

@@

Several previous works on making machine translation systems between
Turkic languages exist, although to our knowledge none are publically available.
For systems between Turkish and other Turkic languages, there have been,
for example, systems reported for Turkish-Crimean Tatar \citep{altintas01},
Turkish-Azerbaijani \citep{hamzaoglu93}, Turkish-Tatar \citep{suleymanov08}, and
Turkish-Turkmen \citep{tantug07}.

A prototype Tatar-Bashkir machine translation system was built by ourselves.
Due to the closeness of the languages, it proved to provide high accuracy
translations, but being a prototype system by design, had relatively low
coverage.
